Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added personality disorder positive diagnosis by sample chunk

>>>>

```{r Get personality disorders positive by sample}

dat.retro_PD_by_sample <- dat.retro %>%
  group_by(Sample_plot) %>% 
  select(personality_disorder_numeric) %>% 
  filter(personality_disorder_numeric == 1)

dat.retro_PD_by_sample <- dat.retro_PD_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("Personality disorders" = n())
